\documentclass[letterpaper, 10pt]{letter}
\usepackage{anysize}
\marginsize{1in}{1in}{0.5in}{0.5in}
\usepackage{setspace}
\usepackage{url}
\usepackage{verbatim}
\usepackage{parskip}
\usepackage{hyperref}
\hypersetup{pdfborder={0 0 0}, colorlinks=true, urlcolor=blue}

\newcommand{\ignore}[1]{}
\newcommand{\super}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand{\sub}[1]{\ensuremath{_{\textrm{#1}}}}
\newcommand{\dC}{\ensuremath{^\circ{\textrm{C}}}}

\makeatletter
\let\@texttop\relax
\makeatother

\newenvironment{myEnumerate}{
  \begin{enumerate}
    \setlength{\itemsep}{1pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}}
  {\end{enumerate}}

\newenvironment{myItemize}{
  \begin{itemize}
    \setlength{\itemsep}{1pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}}
  {\end{itemize}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\signature{Jamie Oaks \\ 
                 Biodiversity Institute \\ 
                 University of Kansas \\ 
                 Dyche Hall, 1345 Jayhawk Blvd \\ 
                 Lawrence, KS 66045 \\ 
                 \href{mailto:joaks1@ku.edu}{\texttt{joaks1@ku.edu}} \\ 
                 785-864-3439}
%\address{Biodiversity Institute \\ University of Kansas \\ Dyche Hall, 1345
                 %Jayhawk Blvd \\ Lawrence, KS 66045}
\begin{document}
\begin{letter}{Dr.\ Christopher Yahnke \\
                     Chair, Department of Biology \\
                     University of Wisconsin-Stevens Point \\
                     Stevens Point, WI  54481}
\opening{Dear Dr.\ Yahnke and Members of the Search Committee:}
\raggedright
Please consider my application for the Assistant Professorship in Herpetology
in the Department of Biology at the University of Wisconsin-Stevens Point.
I am extremely excited by this opportunity, because of the wealth of potential
resources and colleagues in your department, and the chance to return to my
home state of Wisconsin, where my family resides.
I am currently a Ph.D.\ candidate under the direction of Drs.\ Rafe Brown and
Mark Holder in the Department of Ecology and Evolutionary Biology at the
University of Kansas.
I am on track to complete my degree in Spring of 2013, but can expedite my
completion to Fall of 2012 if the position requires.

I am a broadly trained biologist who studies the evolutionary genetics of
reptiles and amphibians.
My research program uses genomic variation within and among species to
investigate the processes that generate biodiversity and promote and constrain
adaptation.
My research is quantitative and integrative, incorporating concepts and
techniques from phylogenetics, population genetics, genomics, bioinformatics,
and computer science.

While my research program is geographically focused in Southeast Asia, I grew
up catching reptiles and amphibians in Wisconsin, and I am keenly interested in
developing projects in the Upper Midwest.
I am particularly excited by your department's extensive field resources and
Herpetology Collection, which will undoubtedly help in establishing a local
research program.
I would love the opportunity to foster and grow the Vertebrate Collections at
UW-Stevens Point through active, collections-based research both locally and
internationally.

My qualifications for this faculty position include successful acquisition of
funding for my research program.
During my graduate career, I have secured more than \$45,600 that I received in
fellowships and grants through the 
National Science Foundation,
Society of Systematic Biologists,
Sigma Xi Scientific Research Society,
Louisiana State University Department of Biological Sciences and Museum of
Natural Science,
and University of Kansas Office of Graduate Studies, EEB Department and
Biodiversity Institute.
To date, my research has resulted in five publications, including a
senior-authored publication in
\href{http://onlinelibrary.wiley.com/doi/10.1111/j.1558-5646.2011.01373.x/abstract}{\it
Evolution} that was featured on the journal's cover and in
\href{http://www.nature.com/nature/journal/v474/n7353/full/474545a.html}{\it
Nature}. 

I am strongly committed to teaching and mentoring undergraduate and graduate
students.
Through my experiences as a tutor, teaching assistant, and guest lecturer, I
have developed a strong passion for teaching science.
I recently received an Award for Excellence in Teaching from the University of
Kansas Division of Biological Sciences for teaching the discussion sections of
an undergraduate genetics course.
As a graduate student, I have mentored local high school students, KU
undergraduates, and both undergraduate and graduate students in Malaysia in the
methods of field-based biodiversity research.
Under my mentorship, Liz Lusher, a KU undergraduate, secured an Undergraduate
Research Award and successfully completed a phylogeographic study of ringneck
snakes across the Great Plains.

As a faculty member, I will strive to be a well-funded, productive researcher,
collaborative colleague, passionate teacher, and supportive advisor.
My diverse and integrative research interests, as well as my commitment to
teaching and mentoring, would be an asset to the Biology Department at the
University of Wisconsin-Stevens Point.
%After reviewing my application materials, I hope you will strongly consider me
%for the position.

I have requested letters of support from Drs.\ Rafe Brown
(\href{mailto:rafe@ku.edu}{\tt rafe@ku.edu}), Mark Holder
(\href{mailto:mtholder@ku.edu}{\tt mtholder@ku.edu}), and Lee Grismer
(\href{mailto:lgrismer@lasierra.edu}{\tt lgrismer@lasierra.edu}), and
transcripts from the University of Wisconsin Oshkosh, Louisiana State
University, and the University of Kansas.
Upon request, I am happy to provide a copy of my manuscripts that are currently
in review or in press.
Thank you for considering my application, and I look forward to speaking with
you about this position.
Please do not hesitate to contact me if you have any questions.

\addtolength{\medskipamount}{-5pt}
\closing{Sincerely,}
\end{letter}
\end{document}

